### 2023-03-29 response-to-audit-report.md

 instance Eq a => Eq (Value a) where
     {-# INLINABLE (==) #-}
-    AvailableMoney acc1 tok1 == AvailableMoney acc2 tok2 =
-        acc1 == acc2 && tok1 == tok2
+    AvailableMoney acc1 tok1 == AvailableMoney acc2 tok2 = acc1 == acc2 && tok1 == tok2
+    AvailableMoney _    _    == _                        = False
     Constant i1 == Constant i2 = i1 == i2
+    Constant{}  == _           = False
     NegValue val1 == NegValue val2 = val1 == val2
+    NegValue{}    == _             = False
     AddValue val1 val2 == AddValue val3 val4 = val1 == val3 && val2 == val4
+    AddValue{}         == _                  = False
     SubValue val1 val2 == SubValue val3 val4 = val1 == val3 && val2 == val4
+    SubValue{}         == _                  = False
     MulValue val1 val2 == MulValue val3 val4 = val1 == val3 && val2 == val4
+    MulValue{}         == _                  = False
     DivValue val1 val2 == DivValue val3 val4 = val1 == val3 && val2 == val4
+    DivValue{}         == _                  = False
     ChoiceValue cid1 == ChoiceValue cid2 = cid1 == cid2
+    ChoiceValue{}    == _                = False
     TimeIntervalStart == TimeIntervalStart = True
-    TimeIntervalEnd   == TimeIntervalEnd   = True
+    TimeIntervalStart == _                 = False
+    TimeIntervalEnd == TimeIntervalEnd = True
+    TimeIntervalEnd == _               = False
     UseValue val1 == UseValue val2 = val1 == val2
-    Cond obs1 thn1 els1 == Cond obs2 thn2 els2 =  obs1 == obs2 && thn1 == thn2 && els1 == els2
-    _ == _ = False
+    UseValue{}    == _             = False
+    Cond obs1 thn1 els1 == Cond obs2 thn2 els2 = obs1 == obs2 && thn1 == thn2 && els1 == els2
+    Cond{}              == _                   = False

 instance Eq Observation where
     {-# INLINABLE (==) #-}
     AndObs o1l o2l == AndObs o1r o2r           = o1l == o1r && o2l == o2r
+    AndObs{}       == _                        = False
     OrObs  o1l o2l == OrObs  o1r o2r           = o1l == o1r && o2l == o2r
+    OrObs{}        == _                        = False
     NotObs ol == NotObs or                     = ol == or
+    NotObs{}  == _                             = False
     ChoseSomething cid1 == ChoseSomething cid2 = cid1 == cid2
+    ChoseSomething _    == _                   = False
     ValueGE v1l v2l == ValueGE v1r v2r         = v1l == v1r && v2l == v2r
+    ValueGE{}       == _                       = False
     ValueGT v1l v2l == ValueGT v1r v2r         = v1l == v1r && v2l == v2r
+    ValueGT{}       == _                       = False
     ValueLT v1l v2l == ValueLT v1r v2r         = v1l == v1r && v2l == v2r
+    ValueLT{}       == _                       = False
     ValueLE v1l v2l == ValueLE v1r v2r         = v1l == v1r && v2l == v2r
+    ValueLE{}       == _                       = False
     ValueEQ v1l v2l == ValueEQ v1r v2r         = v1l == v1r && v2l == v2r
+    ValueEQ{}       == _                       = False
     TrueObs  == TrueObs                        = True
+    TrueObs  == _                              = False
     FalseObs == FalseObs                       = True
-    _ == _                                     = False
+    FalseObs == _                              = False

 instance Eq Action where
     {-# INLINABLE (==) #-}
     Deposit acc1 party1 tok1 val1 == Deposit acc2 party2 tok2 val2 =
         acc1 == acc2 && party1 == party2 && tok1 == tok2 && val1 == val2
+    Deposit{}       == _ = False
     Choice cid1 bounds1 == Choice cid2 bounds2 =
         cid1 == cid2 && length bounds1 == length bounds2 && let
             bounds = zip bounds1 bounds2
             checkBound (Bound low1 high1, Bound low2 high2) = low1 == low2 && high1 == high2
             in all checkBound bounds
+    Choice{}   == _ = False
     Notify obs1 == Notify obs2 = obs1 == obs2
-    _ == _ = False
+    Notify{} == _ = False

 instance Eq a => Eq (Case a) where
     {-# INLINABLE (==) #-}
     Case acl cl == Case acr cr                       = acl == acr && cl == cr
+    Case{}      == _                                 = False
     MerkleizedCase acl bsl == MerkleizedCase acr bsr = acl == acr && bsl == bsr
-    _ == _                                           = False
+    MerkleizedCase{}       == _                      = False

 instance Eq Contract where
     {-# INLINABLE (==) #-}
     Close == Close = True
+    Close == _ = False
     Pay acc1 payee1 tok1 value1 cont1 == Pay acc2 payee2 tok2 value2 cont2 =
         acc1 == acc2 && payee1 == payee2 && tok1 == tok2 && value1 == value2 && cont1 == cont2
+    Pay{} == _ = False
     If obs1 cont1 cont2 == If obs2 cont3 cont4 =
         obs1 == obs2 && cont1 == cont3 && cont2 == cont4
-    When cases1 timeout1 cont1 == When cases2 timeout2 cont2 =
+    If{} == _ = False
+    When cases1 timeout1 cont1 == When cases2 timeout2 cont2 =  -- The sequences of tests are ordered for efficiency.
         timeout1 == timeout2 && cont1 == cont2
         && length cases1 == length cases2
         && and (zipWith (==) cases1 cases2)
+    When{} == _ = False
     Let valId1 val1 cont1 == Let valId2 val2 cont2 =
         valId1 == valId2 && val1 == val2 && cont1 == cont2
+    Let{} == _ = False
     Assert obs1 cont1 == Assert obs2 cont2 = obs1 == obs2 && cont1 == cont2
-    _ == _ = False
+    Assert{}  == _ = False

 instance Eq State where
diff --git a/marlowe/src/Language/Marlowe/Scripts.hs b/marlowe/src/Language/Marlowe/Scripts.hs
index 6027202b5..aa397d5fa 100644
--- a/marlowe/src/Language/Marlowe/Scripts.hs
+++ b/marlowe/src/Language/Marlowe/Scripts.hs
@@ -47,7 +47,9 @@ module Language.Marlowe.Scripts
   , alternateMarloweValidator
   , alternateMarloweValidatorHash
   , marloweValidator
+  , marloweValidatorCompiled
   , marloweValidatorHash
+  , mkMarloweValidator
     -- * Payout Validator
   , TypedRolePayoutValidator
   , rolePayoutValidator
@@ -61,8 +63,9 @@ import GHC.Generics (Generic)
 import Language.Marlowe.Core.V1.Semantics as Semantics
 import Language.Marlowe.Core.V1.Semantics.Types as Semantics
 import Language.Marlowe.Pretty (Pretty(..))
+import Ledger.Typed.Scripts (unsafeMkTypedValidator)
 import qualified Plutus.Script.Utils.Typed as Scripts
-import Plutus.Script.Utils.V2.Typed.Scripts (mkTypedValidator, mkUntypedValidator)
+import Plutus.Script.Utils.V2.Typed.Scripts (mkTypedValidator)
 import qualified Plutus.Script.Utils.V2.Typed.Scripts as Scripts
 import qualified Plutus.V1.Ledger.Address as Address (scriptHashAddress)
 import qualified Plutus.V1.Ledger.Value as Val
@@ -92,11 +95,22 @@ import PlutusTx (makeIsDataIndexed, makeLift)
 import qualified PlutusTx
 import qualified PlutusTx.AssocMap as AssocMap
 import PlutusTx.Plugin ()
-import PlutusTx.Prelude as PlutusTxPrelude
+import PlutusTx.Prelude as PlutusTxPrelude hiding (traceError, traceIfFalse)
 import qualified Prelude as Haskell
 import Unsafe.Coerce (unsafeCoerce)

+-- Suppress traces, in order to save bytes.
+
+{-# INLINABLE traceError #-}
+traceError :: BuiltinString -> a
+traceError _ = error ()
+
+{-# INLINABLE traceIfFalse #-}
+traceIfFalse :: BuiltinString -> a -> a
+traceIfFalse _ = id
+
+
 -- | Input to a Marlowe transaction.
 type MarloweInput = [MarloweTxInput]

@@ -136,7 +150,7 @@ rolePayoutValidator = mkTypedValidator @TypedRolePayoutValidator
   $$(PlutusTx.compile [|| mkRolePayoutValidator ||])
   $$(PlutusTx.compile [|| wrap ||])
   where
-    wrap = Scripts.mkUntypedValidator @(CurrencySymbol, TokenName) @()
+    wrap = Scripts.mkUntypedValidator @_ @(CurrencySymbol, TokenName) @()

 {-# INLINABLE rolePayoutValidator #-}
@@ -147,7 +161,7 @@ mkRolePayoutValidator :: (CurrencySymbol, TokenName)  -- ^ The datum is the curr
                       -> Bool                         -- ^ Whether the transaction validated.
 mkRolePayoutValidator (currency, role) _ ctx =
     -- The role token for the correct currency must be present.
-    -- [Marlowe-Cardano Specification: "16. Payment authorized".]
+    -- [Marlowe-Cardano Specification: "17. Payment authorized".]
     Val.singleton currency role 1 `Val.leq` valueSpent (scriptContextTxInfo ctx)

@@ -188,12 +202,10 @@ mkMarloweValidator
             case closeInterval $ txInfoValidRange scriptContextTxInfo of
                 Just interval' -> interval'
                 Nothing        -> traceError "a"
-    -- The incoming balance of each account must be positive.
-    -- [Marlowe-Cardano Specification: "Constraint 13. Positive balances".]
-    let positiveBalances = traceIfFalse "b" $ validateBalances marloweState

     -- Find Contract continuation in TxInfo datums by hash or fail with error.
     let inputs = fmap marloweTxInputToInput marloweTxInputs
+
     {-  We do not check that a transaction contains exact input payments.
         We only require an evidence from a party, e.g. a signature for PubKey party,
         or a spend of a 'party role' token.  This gives huge flexibility by allowing
@@ -201,22 +213,19 @@ mkMarloweValidator
         Then, we check scriptOutput to be correct.
      -}
     let inputContents = fmap getInputContent inputs
+
     -- Check that the required signatures and role tokens are present.
     -- [Marlowe-Cardano Specification: "Constraint 14. Inputs authorized".]
-    let inputsOk = validateInputs inputContents
-
-    -- Since individual balances were validated to be positive,
-    -- the total balance is also positive.
-    let inputBalance = totalBalance (accounts marloweState)
+    let inputsOk = allInputsAreAuthorized inputContents

     -- [Marlowe-Cardano Specification: "Constraint 5. Input value from script".]
-    -- The total incoming balance must match the actual script value being spent.
-    let balancesOk = traceIfFalse "v" $ inputBalance == scriptInValue
-
-    let preconditionsOk = positiveBalances && balancesOk
+    -- [Marlowe-Cardano Specification: "Constraint 13. Positive balances".]
+    -- [Marlowe-Cardano Specification: "Constraint 19. No duplicates".]
+    -- Check that the initial state obeys the Semantic's invariants.
+    let preconditionsOk = checkState "i" scriptInValue marloweState

-    -- Package the inputs to be applied in the semantics.
     -- [Marlowe-Cardano Specification: "Constraint 0. Input to semantics".]
+    -- Package the inputs to be applied in the semantics.
     let txInput = TransactionInput {
             txInterval = interval,
             txInputs = inputs }
@@ -246,16 +255,25 @@ mkMarloweValidator

                 checkContinuation = case txOutContract of
                     -- [Marlowe-Cardano Specification: "Constraint 4. No output to script on close".]
-                    Close -> traceIfFalse "c" checkScriptOutputAny
+                    Close -> traceIfFalse "c" hasNoOutputToOwnScript
                     _ -> let
                         totalIncome = foldMap collectDeposits inputContents
                         totalPayouts = foldMap snd payoutsByParty
-                        finalBalance = inputBalance + totalIncome - totalPayouts
-                        -- The total account balance must be paid to a single output to the script.
-                        -- [Marlowe-Cardano Specification: "Constraint 3. Single Marlowe output".]
-                        -- [Marlowe-Cardano Specification: "Constraint 6. Output value to script."]
-                        in checkOwnOutputConstraint marloweData finalBalance
+                        finalBalance = scriptInValue + totalIncome - totalPayouts
+                        in
+                             -- [Marlowe-Cardano Specification: "Constraint 3. Single Marlowe output".]
+                             -- [Marlowe-Cardano Specification: "Constraint 6. Output value to script."]
+                             -- Check that the single Marlowe output has the correct datum and value.
+                             checkOwnOutputConstraint marloweData finalBalance
+                             -- [Marlowe-Cardano Specification: "Constraint 18. Final balance."]
+                             -- [Marlowe-Cardano Specification: "Constraint 13. Positive balances".]
+                             -- [Marlowe-Cardano Specification: "Constraint 19. No duplicates".]
+                             -- Check that the final state obeys the Semantic's invariants.
+                          && checkState "o" finalBalance txOutState
             preconditionsOk && inputsOk && payoutsOk && checkContinuation
+              -- [Marlowe-Cardano Specification: "20. Single satsifaction".]
+              -- Either there must be no payouts, or there must be no other validators.
+              && traceIfFalse "z" (null payoutsByParty || noOthers)
         Error TEAmbiguousTimeIntervalError -> traceError "i"
         Error TEApplyNoMatchError -> traceError "n"
         Error (TEIntervalError (InvalidInterval _)) -> traceError "j"
@@ -274,24 +292,73 @@ mkMarloweValidator
         find (\TxInInfo{txInInfoOutRef} -> txInInfoOutRef == txOutRef) txInfoInputs
     findOwnInput _ = Nothing

-    -- The inputs being spent by this script.
     -- [Marlowe-Cardano Specification: "2. Single Marlowe script input".]
+    -- The inputs being spent by this script, and whether other validators are present.
     ownInput :: TxInInfo
-    ownInput@TxInInfo{txInInfoResolved=TxOut{txOutAddress=ownAddress}} =
+    noOthers :: Bool
+    (ownInput@TxInInfo{txInInfoResolved=TxOut{txOutAddress=ownAddress}}, noOthers) =
         case findOwnInput ctx of
-            Just ownTxInInfo ->
-                case filter (sameValidatorHash ownTxInInfo) (txInfoInputs scriptContextTxInfo) of
-                    [i] -> i
-                    _   -> traceError "w" -- Multiple Marlowe contract inputs with the same address are forbidden.
+            Just ownTxInInfo -> examineScripts (sameValidatorHash ownTxInInfo) Nothing True (txInfoInputs scriptContextTxInfo)
             _ -> traceError "x" -- Input to be validated was not found.

+    -- Check for the presence of multiple Marlowe validators or other Plutus validators.
+    examineScripts
+      :: (ValidatorHash -> Bool)  -- Test for this validator.
+      -> Maybe TxInInfo           -- The input for this validator, if found so far.
+      -> Bool                     -- Whether no other validator has been found so far.
+      -> [TxInInfo]               -- The inputs remaining to be examined.
+      -> (TxInInfo, Bool)         -- The input for this validator and whehter no other validators are present.
+    -- This validator has not been found.
+    examineScripts _ Nothing _ [] = traceError "x"
+    -- This validator has been found, and other validators may have been found.
+    examineScripts _ (Just self) noOthers [] = (self, noOthers)
+    -- Found both this validator and another script, so we short-cut.
+    examineScripts _ (Just self) False _ = (self, False)
+     -- Found one script.
+    examineScripts f mSelf noOthers (tx@TxInInfo{txInInfoResolved=TxOut{txOutAddress=Ledger.Address (ScriptCredential vh) _}} : txs)
+      -- The script is this validator.
+      | f vh = case mSelf of
+                 -- We hadn't found it before, so we save it in `mSelf`.
+                 Nothing -> examineScripts f (Just tx) noOthers txs
+                 -- We already had found this validator before
+                 Just _ -> traceError "w"
+      -- The script is something else, so we set `noOther` to `False`.
+      | otherwise = examineScripts f mSelf False txs
+    -- An input without a validator is encountered.
+    examineScripts f self others (_ : txs) = examineScripts f self others txs
+
     -- Check if inputs are being spent from the same script.
-    sameValidatorHash:: TxInInfo -> TxInInfo -> Bool
-    sameValidatorHash
-        TxInInfo{txInInfoResolved=TxOut{txOutAddress=Ledger.Address (ScriptCredential vh1) _}}
-        TxInInfo{txInInfoResolved=TxOut{txOutAddress=Ledger.Address (ScriptCredential vh2) _}} = vh1 == vh2
+    sameValidatorHash:: TxInInfo -> ValidatorHash -> Bool
+    sameValidatorHash TxInInfo{txInInfoResolved=TxOut{txOutAddress=Ledger.Address (ScriptCredential vh1) _}} vh2 = vh1 == vh2
     sameValidatorHash _ _ = False

### 2023-03-29 response-to-audit-report.md

+    -- Check a state for the correct value, positive accounts, and no duplicates.
+    checkState :: BuiltinString -> Val.Value -> State -> Bool
+    checkState tag expected State{..} =
+      let
+        positiveBalance :: (a, Integer) -> Bool
+        positiveBalance (_, balance) = balance > 0
+        noDuplicates :: Eq k => AssocMap.Map k v -> Bool
+        noDuplicates am =
+          let
+            test [] = True           -- An empty list has no duplicates.
+            test (x : xs)            -- Look for a duplicate of the head in the tail.
+              | elem x xs = False    -- A duplicate is present.
+              | otherwise = test xs  -- Continue searching for a duplicate.
+          in
+            test $ AssocMap.keys am
+      in
+           -- [Marlowe-Cardano Specification: "Constraint 5. Input value from script".]
+           -- and/or
+           -- [Marlowe-Cardano Specification: "Constraint 18. Final balance."]
+           traceIfFalse ("v"  <> tag) (totalBalance accounts == expected)
+           -- [Marlowe-Cardano Specification: "Constraint 13. Positive balances".]
+        && traceIfFalse ("b"  <> tag) (all positiveBalance $ AssocMap.toList accounts)
+           -- [Marlowe-Cardano Specification: "Constraint 19. No duplicates".]
+        && traceIfFalse ("ea" <> tag) (noDuplicates accounts)
+        && traceIfFalse ("ec" <> tag) (noDuplicates choices)
+        && traceIfFalse ("eb" <> tag) (noDuplicates boundValues)
+
     -- Look up the Datum hash for specific data.
     findDatumHash' :: PlutusTx.ToData o => o -> Maybe DatumHash
     findDatumHash' datum = findDatumHash (Datum $ PlutusTx.toBuiltinData datum) scriptContextTxInfo
@@ -301,7 +368,7 @@ mkMarloweValidator
     checkOwnOutputConstraint ocDatum ocValue =
         let hsh = findDatumHash' ocDatum
         in traceIfFalse "d" -- "Output constraint"
-        $ checkScriptOutput ownAddress hsh ocValue getContinuingOutput
+        $ checkScriptOutput (==) ownAddress hsh ocValue getContinuingOutput

     getContinuingOutput :: TxOut
     getContinuingOutput = case filter (\TxOut{txOutAddress} -> ownAddress == txOutAddress) allOutputs of
@@ -309,20 +376,14 @@ mkMarloweValidator
         _     -> traceError "o" -- No continuation or multiple Marlowe contract outputs is forbidden.

     -- Check that address, value, and datum match the specified.
-    checkScriptOutput :: Ledger.Address -> Maybe DatumHash -> Val.Value -> TxOut -> Bool
-    checkScriptOutput addr hsh value TxOut{txOutAddress, txOutValue, txOutDatum=OutputDatumHash svh} =
-                    txOutValue == value && hsh == Just svh && txOutAddress == addr
-    checkScriptOutput _ _ _ _ = False
-
-    -- Check that address and datum match the specified, and that value is at least that required.
-    checkScriptOutputRelaxed :: Ledger.Address -> Maybe DatumHash -> Val.Value -> TxOut -> Bool
-    checkScriptOutputRelaxed addr hsh value TxOut{txOutAddress, txOutValue, txOutDatum=OutputDatumHash svh} =
-                    txOutValue `Val.geq` value && hsh == Just svh && txOutAddress == addr
-    checkScriptOutputRelaxed _ _ _ _ = False
+    checkScriptOutput :: (Val.Value -> Val.Value -> Bool) -> Ledger.Address -> Maybe DatumHash -> Val.Value -> TxOut -> Bool
+    checkScriptOutput comparison addr hsh value TxOut{txOutAddress, txOutValue, txOutDatum=OutputDatumHash svh} =
+                    txOutValue `comparison` value && hsh == Just svh && txOutAddress == addr
+    checkScriptOutput _ _ _ _ _ = False

     -- Check for any output to the script address.
-    checkScriptOutputAny :: Bool
-    checkScriptOutputAny = all ((/= ownAddress) . txOutAddress) allOutputs
+    hasNoOutputToOwnScript :: Bool
+    hasNoOutputToOwnScript = all ((/= ownAddress) . txOutAddress) allOutputs

     -- All of the script outputs.
     allOutputs :: [TxOut]
@@ -339,8 +400,8 @@ mkMarloweValidator
     marloweTxInputToInput (Input input) = NormalInput input

     -- Check that inputs are authorized.
-    validateInputs :: [InputContent] -> Bool
-    validateInputs = all validateInputWitness
+    allInputsAreAuthorized :: [InputContent] -> Bool
+    allInputsAreAuthorized = all validateInputWitness
       where
         validateInputWitness :: InputContent -> Bool
         validateInputWitness input =
@@ -356,8 +417,10 @@ mkMarloweValidator

     -- Tally the deposits in the input.
     collectDeposits :: InputContent -> Val.Value
-    collectDeposits (IDeposit _ _ (Token cur tok) amount) = Val.singleton cur tok amount
-    collectDeposits _                                     = zero
+    collectDeposits (IDeposit _ _ (Token cur tok) amount)
+      | amount > 0    = Val.singleton cur tok amount  -- SCP-5123: Semantically negative deposits
+      | otherwise     = zero                          -- do not remove funds from the script's UTxO.
+    collectDeposits _ = zero

     -- Extract the payout to a party.
     payoutByParty :: Payment -> AssocMap.Map Party Val.Value
@@ -374,12 +437,17 @@ mkMarloweValidator
       where
         payoutToTxOut :: (Party, Val.Value) -> Bool
         payoutToTxOut (party, value) = case party of
+            -- [Marlowe-Cardano Specification: "Constraint 15. Sufficient Payment".]
+            -- SCP-5128: Note that the payment to an address may be split into several outputs but the payment to a role must be
+            -- a single output. The flexibily of multiple outputs accommodates wallet-related practicalities such as the change and
+            -- the return of the role token being in separate UTxOs in situations where a contract is also paying to the address
+            -- where that change and that role token are sent.
             Address _ address  -> traceIfFalse "p" $ value `Val.leq` valuePaidToAddress address  -- At least sufficient value paid.
             Role role -> let
                 hsh = findDatumHash' (rolesCurrency, role)
                 addr = Address.scriptHashAddress rolePayoutValidatorHash
                 -- Some output must have the correct value and datum to the role-payout address.
-                in traceIfFalse "r" $ any (checkScriptOutputRelaxed addr hsh value) allOutputs
+                in traceIfFalse "r" $ any (checkScriptOutput Val.geq addr hsh value) allOutputs

     -- The key for the address must have signed.
     txSignedByAddress :: Ledger.Address -> Bool
@@ -402,7 +470,7 @@ marloweValidator :: Scripts.TypedValidator TypedMarloweValidator
 marloweValidator =
   let
     mkUntypedMarloweValidator :: ValidatorHash -> BuiltinData -> BuiltinData -> BuiltinData -> ()
-    mkUntypedMarloweValidator rp = mkUntypedValidator (mkMarloweValidator rp)
+    mkUntypedMarloweValidator rp = Scripts.mkUntypedValidator (mkMarloweValidator rp)

     untypedValidator :: Scripts.Validator
     untypedValidator = mkValidatorScript $
@@ -410,10 +478,20 @@ marloweValidator =
         `PlutusTx.applyCode` PlutusTx.liftCode rolePayoutValidatorHash

     typedValidator :: Scripts.TypedValidator Scripts.Any
-    typedValidator = Scripts.unsafeMkTypedValidator untypedValidator
+    typedValidator = unsafeMkTypedValidator (Scripts.Versioned untypedValidator Scripts.PlutusV2)
   in
     unsafeCoerce typedValidator

+
+marloweValidatorCompiled :: PlutusTx.CompiledCode (ValidatorHash -> PlutusTx.BuiltinData -> PlutusTx.BuiltinData -> PlutusTx.BuiltinData -> ())
+marloweValidatorCompiled =
+  let
+    mkUntypedMarloweValidator :: ValidatorHash -> PlutusTx.BuiltinData -> PlutusTx.BuiltinData -> PlutusTx.BuiltinData -> ()
+    mkUntypedMarloweValidator rp = Scripts.mkUntypedValidator (mkMarloweValidator rp)
+  in
+    $$(PlutusTx.compile [|| mkUntypedMarloweValidator ||])
+
+
 -- | The hash of the Marlowe semantics validator.
 marloweValidatorHash :: ValidatorHash
 marloweValidatorHash = Scripts.validatorHash marloweValidator
@@ -432,7 +510,7 @@ alternateMarloweValidator = Scripts.mkTypedValidator
           $$(PlutusTx.compile [|| mkMarloweValidator ||])
             `PlutusTx.applyCode`
               PlutusTx.liftCode rolePayoutValidatorHash
-        mkArgsValidator = mkUntypedValidator @MarloweData @MarloweInput
+        mkArgsValidator = Scripts.mkUntypedValidator @_ @MarloweData @MarloweInput
         compiledArgsValidator =
           $$(PlutusTx.compile [|| mkArgsValidator ||])
```

### Post-Audit Changes in Property-Based Tests for Marlowe Validator

```bash
git diff 523f3d56f22bf992ddb0b0c8a52bb7a5a188f9e9 69468d6623e24a4ccd6659e378ae012c38ca01ce marlowe-test/src/
```

```diff
diff --git a/marlowe-test/src/Data/Jsonable.hs b/marlowe-test/src/Data/Jsonable.hs
new file mode 100644
index 000000000..b16e3e044
--- /dev/null
+++ b/marlowe-test/src/Data/Jsonable.hs
@@ -0,0 +1,126 @@
+-----------------------------------------------------------------------------
+--
+-- Module      :  $Headers
+-- License     :  Apache 2.0
+--
+-- Stability   :  Experimental
+-- Portability :  Portable
+--
+-- | Wrapping values that can be converted to and from JSON.
+--
+-----------------------------------------------------------------------------
+
+
+{-# LANGUAGE ExistentialQuantification #-}
+{-# LANGUAGE OverloadedStrings #-}
+{-# LANGUAGE RecordWildCards #-}
+{-# LANGUAGE ScopedTypeVariables #-}
+
+
+module Data.Jsonable
+  ( -- * Types
+    Jsonable(..)
+  , JsonableType(..)
+  , KnownJsonable
+    -- * Conversion
+  , fromJsonable
+  , isKnownJson
+  , toJsonable
+    -- * Testing
+  , arbitraryJsonable
+  , checkRoundTripJsonable
+  , generateJsonable
+  , roundTripJsonable
+  ) where
+
+
+import Data.Aeson (FromJSON(..), Result(..), ToJSON(..), Value, fromJSON)
+import Data.Proxy (Proxy(..))
+import Test.Tasty.QuickCheck (Arbitrary(..), Gen)
+
+
+-- | A list of known types with `FromJSON`, `ToJSON`, and `Arbitrary` instances.
+type KnownJsonable = [JsonableType]
+
+
+-- | A type with `FromJSON`, `ToJSON`, and `Arbitrary` instances.
+data JsonableType = forall a. (ToJSON a, FromJSON a, Arbitrary a) => JsonableType {typeKey :: String, typeValue :: Proxy a}
+
+
+-- | A value with `FromJSON`, `ToJSON`, and `Arbitrary` instances.
+data Jsonable = forall a . (ToJSON a, FromJSON a, Arbitrary a) => Jsonable {jsonableType :: String, jsonableValue :: a}
+
+
+-- | Deserialize a JSON value.
+toJsonable
+  :: KnownJsonable  -- ^ A list of known types with `FromJSON`, `ToJSON`, and `Arbitrary` instances.
+  -> String   -- ^ The key for the type.
+  -> Value  -- ^ The JSON value.
+  -> Either String Jsonable  -- ^ The deserialized value, or an error message.
+toJsonable known s v =
+  let
+    fromJson' :: forall a . FromJSON a => Proxy a -> Either String a
+    fromJson' _ =
+      case fromJSON v :: Result a of
+        Success x -> Right x
+        Error msg -> Left msg
+  in
+    case filter ((s ==) . typeKey) known of
+      [JsonableType{..}] -> Jsonable typeKey <$> fromJson' typeValue
+      _                  -> Left $ "JSON serialization not supported for " <> s <> "."
+
+
+-- | Check for a known JSON type.
+isKnownJson
+  :: KnownJsonable  -- ^ A list of known types with `FromJSON`, `ToJSON`, and `Arbitrary` instances.
+  -> String   -- ^ The key for the type.
+  -> Bool  -- ^ Whether the type is in the list of known JSON types.
+isKnownJson known s = length (filter ((s ==) . typeKey) known) == 1
+
+
+-- | Serialize a JSON value.
+fromJsonable
+  :: Jsonable  -- ^ The value.
+  -> Value  -- ^ The JSON.
+fromJsonable Jsonable{..} = toJSON jsonableValue
+
+
+-- | Peform round-trip deserialization and serialization of a JSON value.
+roundTripJsonable
+  :: KnownJsonable  -- ^ A list of known types with `FromJSON`, `ToJSON`, and `Arbitrary` instances.
+  -> String  -- ^ The key for the type.
+  -> Value  -- ^ The JSON value.
+  -> Either String Value  -- ^ There the re-serialized value, or an error message.
+roundTripJsonable known = (fmap fromJsonable .) . toJsonable known
+
+
+-- | Check that round-trip re-serialization doesn't alter a JSON value.
+checkRoundTripJsonable
+  :: KnownJsonable  -- ^ A list of known types with `FromJSON`, `ToJSON`, and `Arbitrary` instances.
+  -> String  -- ^ The key for the type.
+  -> Value  -- ^ The JSON value.
+  -> Bool  -- ^ Whether the JSON value is unchanged.
+checkRoundTripJsonable known s v = roundTripJsonable known s v == Right v
+
+
+-- | Generate an arbitrary value.
+arbitraryJsonable
+  :: JsonableType  -- ^ The type to generate.
+  -> Gen Jsonable  -- ^ The generator.
+arbitraryJsonable JsonableType{..} =
+  let
+    gen :: Arbitrary a => Proxy a -> Gen a
+    gen _ = arbitrary
+  in
+    Jsonable typeKey <$> gen typeValue
+
+
+-- | Generate an arbitrary value.
+generateJsonable
+  :: KnownJsonable  -- ^ A list of known types with `FromJSON`, `ToJSON`, and `Arbitrary` instances.
+  -> String  -- ^ The key for the type.
+  -> Either String (Gen Value)  -- ^ The JSON value.
+generateJsonable known s =
+  case filter ((s ==) . typeKey) known of
+    [jt] -> Right . fmap fromJsonable $ arbitraryJsonable jt
+    _    -> Left $ "JSON serialization not supported for " <> s <> "."
diff --git a/marlowe-test/src/Spec/Marlowe/Common.hs b/marlowe-test/src/Spec/Marlowe/Common.hs
index f52715b5f..77f7ef7cd 100644
--- a/marlowe-test/src/Spec/Marlowe/Common.hs
+++ b/marlowe-test/src/Spec/Marlowe/Common.hs
@@ -12,7 +12,6 @@

 {-# LANGUAGE DataKinds #-}
-{-# LANGUAGE NamedFieldPuns #-}
 {-# LANGUAGE OverloadedStrings #-}
 {-# LANGUAGE ScopedTypeVariables #-}

@@ -490,5 +489,3 @@ pangramContract = let
                 Close)
         , Case (Notify (AndObs (TimeIntervalStart `ValueLT` TimeIntervalEnd) TrueObs)) Close
         ] (Ledger.POSIXTime 100) Close
-
-
diff --git a/marlowe-test/src/Spec/Marlowe/Marlowe.hs b/marlowe-test/src/Spec/Marlowe/Marlowe.hs
index f98e1c899..264b1da93 100644
--- a/marlowe-test/src/Spec/Marlowe/Marlowe.hs
+++ b/marlowe-test/src/Spec/Marlowe/Marlowe.hs
@@ -29,7 +29,6 @@ module Spec.Marlowe.Marlowe
   ) where

-
 import Control.Exception (SomeException, catch)
 import Control.Monad (when)
 import Data.Aeson (decode, eitherDecode, encode)
@@ -151,14 +150,14 @@ alternateMarloweValidatorSize :: IO ()
 alternateMarloweValidatorSize = do
     let validator = Scripts.validatorScript alternateMarloweValidator
     let vsize = SBS.length . SBS.toShort . LB.toStrict $ Serialise.serialise validator
-    assertBool ("alternateMarloweValidator is too large " <> show vsize) (vsize < 15030)
+    assertBool ("alternateMarloweValidator is too large " <> show vsize) (vsize <= 14821)

 -- | Test that the untyped validator is not too large.
 marloweValidatorSize :: IO ()
 marloweValidatorSize = do
     let validator = Scripts.validatorScript marloweValidator
     let vsize = SBS.length . SBS.toShort . LB.toStrict $ Serialise.serialise validator
-    assertBool ("marloweValidator is too large " <> show vsize) (vsize < 12510)
+    assertBool ("marloweValidator is too large " <> show vsize) (vsize <= 12296)

 -- | Test `extractNonMerkleizedContractRoles`.
diff --git a/marlowe-test/src/Spec/Marlowe/Plutus.hs b/marlowe-test/src/Spec/Marlowe/Plutus.hs
index f1a44eaea..ccccdf3c1 100644
--- a/marlowe-test/src/Spec/Marlowe/Plutus.hs
+++ b/marlowe-test/src/Spec/Marlowe/Plutus.hs
@@ -17,9 +17,11 @@ module Spec.Marlowe.Plutus
   ) where

+import Spec.Marlowe.Reference (ReferencePath)
 import Test.Tasty (TestTree, testGroup)

 import qualified Spec.Marlowe.Plutus.AssocMap (tests)
+import qualified Spec.Marlowe.Plutus.MList (tests)
 import qualified Spec.Marlowe.Plutus.Prelude (tests)
 import qualified Spec.Marlowe.Plutus.ScriptContext (tests)
 import qualified Spec.Marlowe.Plutus.Specification (tests)
@@ -27,14 +29,14 @@ import qualified Spec.Marlowe.Plutus.Value (tests)

 -- | Run tests.
-tests :: TestTree
-tests =
+tests :: [ReferencePath] -> TestTree
+tests referencePaths =
   testGroup "Plutus"
     [
       Spec.Marlowe.Plutus.Prelude.tests
     , Spec.Marlowe.Plutus.AssocMap.tests
+    , Spec.Marlowe.Plutus.MList.tests
     , Spec.Marlowe.Plutus.Value.tests
